 

### 2020-10-01 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Temperate and tropical forest canopies are already or will be soon functioning beyond their optimal photosynthetic threshold [@mau_temperate_2018;@huangAirTemperatureOptima2019]. Loss of canopy cover as a result of increasing temperature and related forest disturbances [@senfCanopyMortalityHas2018a; Senfetal.2020] is associated with reductions in canopy structural complexity, and altered microclimates and surface energy balance components [@zellweger_forest_2020; @starkReframingTropicalSavannization2020], this has shown to increase understory temperatures which raises concern for understory species and forest biodiversity [@zellweger_seasonal_2019; @defrenneMicroclimateModeratesPlant2013]

>>>>

Temperate and tropical forest canopies are already or will be soon functioning beyond their optimal photosynthetic threshold [@mau_temperate_2018;@huangAirTemperatureOptima2019]. Loss of canopy cover as a result of increasing temperature and related forest disturbances [@senfCanopyMortalityHas2018a; @senfMappingForestDisturbance2020] is associated with reductions in canopy structural complexity, and altered microclimates and surface energy balance components [@zellweger_forest_2020; @starkReframingTropicalSavannization2020], this has shown to increase understory temperatures which raises concern for understory species and forest biodiversity [@zellweger_seasonal_2019; @defrenneMicroclimateModeratesPlant2013]
